### 2024-05-29 front_materials/acknowledgments.tex
fix grammar

I would like to show my deepest gratitude to my advisor, Prof. Michael Zieve,
for his support and guidance throughout the program.
His valuable insights, during both hard and good times,
has been instrumental in my development a professional mathematician.

I am also profoundly grateful to Prof. Dan Romik for his kindness, dedication, 
and guidance in my research project.
His genuine encouragement was a crucial motivation for me to complete the program,
and his thoughtful feedback with attention to details
significantly improved the presentation of this work.

@@

I am thankful to my friends at Michigan for the memories in Ann Arbor,
that made this town feel like another hometown in the U.S.
I am also grateful to my friends in Korea for their support.
In particular, I am indebted to Hyunwook Nam for his significant help that
made this research possible.

>>>>

I would like to show my deepest gratitude to my advisor, Prof. Michael Zieve,
for his support and guidance throughout the program.
His valuable insights, during both hard and good times,
have been instrumental in my development as a professional mathematician.

I am also profoundly grateful to Prof. Dan Romik for his kindness, dedication, 
and guidance in my research project.
His genuine encouragement was a crucial motivation for me to complete the program,
and his thoughtful feedback with attention to detail
significantly improved the presentation of this work.

@@

I am thankful to my friends in Michigan for the memories in Ann Arbor,
that made this town feel like another hometown in the U.S.
I am also grateful to my friends in Korea for their support.
In particular, I am indebted to Hyunwook Nam for his significant help that
made this research possible.
